\documentclass[10pt,letterpaper,roman]{moderncv}
\moderncvstyle{banking} 
\moderncvcolor{black} 
\renewcommand{\familydefault}{\sfdefault} 
%\nopagenumbers{} 
\usepackage[scale=0.85]{geometry} 

% personal data 
\name{TURE}{PEKEN} 
\phone[mobile]{(520)~8918360} 
\email{turepeken@gmail.com} 
\homepage{turepeken.com} 

\begin{document} 
\makecvtitle 
\vspace*{-10mm} 


%%%%%%%%%%%%  EXPERIENCE %%%%%%%%%%%%
\section{Experience} 
\vspace*{1mm} 

\cventry{May 2018 -- present}{System Engineering Intern}{Keysight Technologies}{Santa Rosa, CA}{} { 
\begin{itemize}%
	\item Developed a demodulator for GFDM (one of the 5G candidate signals) in MATLAB and a macro for VSA to analyze demodulated GFDM signals in C\#.
	\item Developed a blind separation algorithm based on independent component analysis (ICA) in MATLAB for separating undesired signals when measuring a 5G signal. 
	\item Neural network based ICA was implemented for estimating beamforming weight factors of multiple mixed cell signals in FD-MIMO.
\end{itemize}}
\vspace*{1mm} 

\cventry{Aug. 2017 -- Dec. 2017}{Consultant}{Ephibian}{Tucson, AZ}{} { 
\begin{itemize}%
	\item Worked as a consultant for developing CellSim, which is a simulator for cellular networks (GSM, CDMA, UMTS, LTE, WIFI) and it is currently being used as a teaching material for CYBV 479
\end{itemize}} 
\vspace*{1mm} 

\cventry{May 2017 -- Aug. 2017}{R\&D Engineering Intern}{Keysight Technologies}{Santa Rosa, CA}{} { 
\begin{itemize}%
	\item Worked on 5G New Radio Technologies. 
	\item Implemented physical channels and channel encoder for 5G systems based on TS 38.211 and TS 38.212 using MATLAB.
	\item Developed a novel hybrid beamforming algorithm, which was based on map-reduce framework, for 5G and integrated into SystemVue.
\end{itemize}} 
\vspace*{1mm} 

\cventry{May 2016 -- Aug. 2016}{R\&D Engineering Intern}{Keysight Technologies}{Santa Rosa, CA}{} { 
\begin{itemize}%
	\item Worked on channel estimation for massive MIMO which is one of the candidate technologies in 5G.
	\item Implemented pilot-based, semi-blind, and blind channel estimation algorithms by using C++.
	\item Integrated channel estimation algorithms with SystemVue.
	\item This work was presented as a poster titled "Evaluation of Channel Estimation Methods for 5G Radio Interface with Hardware Constraint" in WCNC 2017.
\end{itemize}} 
\vspace*{1mm} 

\cventry{Nov. 2013 -- Sept. 2014}{Software Design Engineer}{Netas}{Istanbul, Turkey}{} { 
\begin{itemize}%
	\item Worked on software design of LTE-Advanced eNodeB for uplink.
	\item Focused on LTE physical layer design and developed channel estimation and equalization algorithms for the receiver of the eNodeB.
	\item Implemented channel estimation and equalization algorithms by using C in Code Composer Studio.
	\item Tested the algorithms on TCI6638K2K which is a DSP model of Texas Instruments.
\end{itemize}} 
\vspace*{1mm} 


%%%%%%%%%%%%  EDUCATION %%%%%%%%%%%%
\section{Education} 

\cventry{Sept. 2014 -- present}
{PhD in Electrical and Computer Engineering} 
{University of Arizona}{Tucson, AZ} 
{GPA:3.78/4.00} 
{\textbf{Coursework}: Network Information Theory with Engineering Applications, Statistical Machine Learning, DSP, Knowledge-Based Systems, Channel Coding, Advanced Topics in Computer Networks, Linear Algebra, Wireless Communications, Theory of Statistics, Independent Study on Millimeter-wave Massive MIMO} 
\vspace*{1mm} 

\cventry{Sept. 2011 -- Dec. 2012}
{Master of Science in Electrical Engineering} 
{University of Michigan}{Ann Arbor, MI} 
{GPA:3.34/4.00} 
{\textbf{Coursework}: Digital Communication and Coding, Communication Networks, Stochastic Processes, Probability, Mathematical Methods for Signal Processing, Game Theory, Real Time Computing} 
\vspace*{1mm} 

\cventry{Sept. 2006 -- Jan 2011}
{Bachelor of Science in Telecommunications Engineering} 
{Istanbul Technical University}{Istanbul, Turkey} 
{GPA:3.78/4.00} 
{Ranked \textbf{3rd} in Telecommunications Engineering} 
\vspace*{1mm} 

\cventry{Sept. 2006 -- May 2011}
{Bachelor of Science in Computer Engineering} 
{Istanbul Technical University}{Istanbul, Turkey} 
{GPA:3.69/4.00} 
{Ranked \textbf{4th}  in Computer Engineering.} 
\vspace*{1mm} 


%%%%%%%%%%%%  Teaching Experience %%%%%%%%%%%%
\section{Teaching Experience} 
\vspace*{1mm} 

\cventry{Jan. 2017 -- May 2018}{Lecturer}{University of Arizona}{Wireless Networking and Security (CYBV 479)}{} { 
\begin{itemize}%
	\item This lecture conforms to the National Security Agency NSA Center of Academic Excellence in Cyber Operations 
	\item Taught wireless technologies, mobile protocols, mobile identifiers, mobile and location-based services, mobile encryption standards, wireless security.
\end{itemize}} 
\vspace*{1mm} 
	
\cventry{Sept. 2015 -- May 2016}{Teaching Assistant}{University of Arizona}{Microprocessor Organization  (ECE 372A)}{} { 
}
\cventry{Jan. 2015 -- May 2015}{Teaching Assistant}{University of Arizona}{Computational Techniques (ECE 330)}{} { 
}
\cventry{Sept. 2014 -- Dec. 2014}{Teaching Assistant}{University of Arizona}{Applications of Engineering Mathematics  (ECE 310)}{} { 
}

%%%%%%%%%%%%  Publications %%%%%%%%%%%%
\section{Publications} 
\cvlistitem{T. Peken, R. Tandon, and T. Bose, "Non-Gaussian Signal Detection: How much can massive MIMO help?", IEEE ICC, 2018.}
\cvlistitem{T. Peken, R. Tandon, and T. Bose, "Map-Reduce Based Hybrid Beamforming: Trade-Off between Complexity and Cost," in in the Proceedings of WInnComm 2017.} 
\cvlistitem{T. Peken, R. Tandon, and T. Bose, "Elastic Net for Channel Estimation in Massive MIMO", in International Telemetering Conference, 2017} 
\cvlistitem{T. Peken, G. Vanhoy, and T. Bose, "Blind Channel Estimation for Massive MIMO," Analog Integrated Circuits and Signal Processing (2017) 91: 257} 
\cvlistitem{T. Peken, M. Hirzallah, and T. Bose, "Effect of Imperfect Channel Estimation on Spectrum Sharing Between the Massive MIMO System and MIMO Radar," in the Proceedings of the SDR-WInnComm, pp. 178 - 182, March 24-26, 2015.}
\cvlistitem{S. Ozen, T. Peken, and S. Oktug, "Energy Efficient Wireless Sensor Network System for Localization", EMERGING 2012, The Fourth International Conference on Emerging Network Intelligence, pp. 43-48.}
\cvlistitem{T. Peken and U. Aygolu, "Adaptive physical layer network coding," 2011 6th International ICST Conference on Communications and Networking in China (CHINACOM), Harbin, 2011, pp. 1146-1150.}


%%%%%%%%%%%%  Awards %%%%%%%%%%%%
\section{Awards}
\cvlistitem{The University of Arizona GPSC Travel Grant for ICC 2018 (May 2018)}

\cvlistitem{College of Engineering Travel Grant for WInnComm 2017 (Nov. 2017)}
\cvlistitem{Poster "Elastic Net for Channel Estimation in Massive MIMO" ranked 3rd in Broadband Wireless Access and Applications Center 2016}
\cvlistitem{Turkish Foundation Education Scholarship (Sept. 2011 -- Dec. 2012)}
\cvlistitem{High Honor List in Istanbul Technical University (Sept. 2006 -- May 2011)}

%%%%%%%%%%%%  Skills %%%%%%%%%%%%
\section{Tehnical Skills} 
\cvlistdoubleitem{MATLAB, C, NesC, C++, QT, C\#}
				 {SystemVue, Signal Studio, VSA}
\cvlistdoubleitem{Python, R, SQL, TinyOS, Assembly}
				 {Eclipse, Netbeans, Visual Studio, Code Composer Studio}
\cvlistdoubleitem{MXG, PXA, Field Fox}
				 {}
				 
\end{document} 


%% NOTLAR
% experience-> PM pozisyonuna uygun sekilde duzenle. "Worker on ... " sonuc ne oldu?
% - NSA toplanti senin contributionlar nasi ekleriz 
% skilleri duzelt
% 

